\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-08-28 msnbase2.Rnw
add keywords and assoc content section
udpate keywords
fix typos identified by rev 4

@@

\begin{figure}[p]
  \centering
<<plot_bench, warning=FALSE, message=FALSE>>=
(p_read + p_sz + p_filt) / p_access +
    plot_layout(heights = c(1, 0.75)) +
    plot_annotation(tag_levels = 'a') &
    theme(axis.title = element_text(size = 10))
@
\caption{(a) Reading time (\textcolor{red}{triplicates,} in seconds)
  and (b) data size in memory (in MB) to read/store 1, 5 and 10 files
  containing 1431 MS1 (on-disk only) and 6103 MS2 (on-disk and
  in-memory) spectra. (c) Filtering benchmark assessed over 10
  interactions on in-memory and on-disk data containing 6103 MS2
  spectra.  (d) Access time to spectra for the in-memory (left) and
  on-disk (right) backends for 1, 10, 100 1000, 5000 and all 6103
  spectra. Benchmarks were performed on a Dell XPS laptop with an
  Intel i5-8250U processor 1.60 GHz (4 cores, 8 threads), 7.5 GB RAM
  running Ubuntu 18.04.4 LTS 64-bit \textcolor{red}{and an SSD
    drive}. \textcolor{red}{The data used for the benchmarking are a
    TMT 4-plex experiment acquired on a LTQ Orbitrap Velos ((Thermo
    Fisher Scientific) available in the \texttt{msdata} package and
    described in \citep{Gatto:2014}.}}
\label{fig:bench}
\end{figure}

@@

The first public commit to the \texttt{MSnbase} GitHub repository was
in October 2010. Since then, the package benefited from 12
contributors\cite{contribs} that added various features, some
particularly significant ones such as the on-disk backend described
herein. \textcolor{red}{Contributions to the package are explicitly
  encouraged, rewarded by an official contributor status and coverned
  by a code of conduct.}

@@

>>>>

Keywords: R, Bioconductor, mass spectrometry, software, metabolomics,
proteomics, visualisation, reproducible research

@@

\begin{figure}[p]
  \centering
<<plot_bench, warning=FALSE, message=FALSE>>=
(p_read + p_sz + p_filt) / p_access +
    plot_layout(heights = c(1, 0.75)) +
    plot_annotation(tag_levels = 'a') &
    theme(axis.title = element_text(size = 10))
@
\caption{(a) Reading time (\textcolor{red}{triplicates,} in seconds)
  and (b) data size in memory (in MB) to read/store 1, 5 and 10 files
  containing 1431 MS1 (on-disk only) and 6103 MS2 (on-disk and
  in-memory) spectra. (c) Filtering benchmark assessed over 10
  interactions on in-memory and on-disk data containing 6103 MS2
  spectra.  (d) Access time to spectra for the in-memory (left) and
  on-disk (right) backends for 1, 10, 100 1000, 5000 and all 6103
  spectra. Benchmarks were performed on a Dell XPS laptop with an
  Intel i5-8250U processor 1.60 GHz (4 cores, 8 threads), 7.5 GB RAM
  running Ubuntu 18.04.4 LTS 64-bit \textcolor{red}{and an SSD
    drive}. \textcolor{red}{The data used for the benchmarking are a
    TMT 4-plex experiment acquired on a LTQ Orbitrap Velos (Thermo
    Fisher Scientific) available in the \texttt{msdata} package and
    described in \citep{Gatto:2014}.}}
\label{fig:bench}
\end{figure}

@@

The first public commit to the \texttt{MSnbase} GitHub repository was
in October 2010. Since then, the package benefited from 12
contributors\cite{contribs} that added various features, some
particularly significant ones such as the on-disk backend described
herein. \textcolor{red}{Contributions to the package are explicitly
  encouraged, rewarded by an official contributor status and governed
  by a code of conduct.}

@@

\section{Associated Content}

Supplementary file 1: script documenting the processing of 1182 mzXML
files (5773464 spectra) using \texttt{MSnbase}.

### 2020-08-28 msnbase2.tex
add keywords and assoc content section
udpate keywords
fix typos identified by rev 4

\end{knitrout}
\caption{(a) Reading time (\textcolor{red}{triplicates,} in seconds)
  and (b) data size in memory (in MB) to read/store 1, 5 and 10 files
  containing 1431 MS1 (on-disk only) and 6103 MS2 (on-disk and
  in-memory) spectra. (c) Filtering benchmark assessed over 10
  interactions on in-memory and on-disk data containing 6103 MS2
  spectra.  (d) Access time to spectra for the in-memory (left) and
  on-disk (right) backends for 1, 10, 100 1000, 5000 and all 6103
  spectra. Benchmarks were performed on a Dell XPS laptop with an
  Intel i5-8250U processor 1.60 GHz (4 cores, 8 threads), 7.5 GB RAM
  running Ubuntu 18.04.4 LTS 64-bit \textcolor{red}{and an SSD
    drive}. \textcolor{red}{The data used for the benchmarking are a
    TMT 4-plex experiment acquired on a LTQ Orbitrap Velos ((Thermo
    Fisher Scientific) available in the \texttt{msdata} package and
    described in \citep{Gatto:2014}.}}
\label{fig:bench}
\end{figure}

>>>>

\end{knitrout}
\caption{(a) Reading time (\textcolor{red}{triplicates,} in seconds)
  and (b) data size in memory (in MB) to read/store 1, 5 and 10 files
  containing 1431 MS1 (on-disk only) and 6103 MS2 (on-disk and
  in-memory) spectra. (c) Filtering benchmark assessed over 10
  interactions on in-memory and on-disk data containing 6103 MS2
  spectra.  (d) Access time to spectra for the in-memory (left) and
  on-disk (right) backends for 1, 10, 100 1000, 5000 and all 6103
  spectra. Benchmarks were performed on a Dell XPS laptop with an
  Intel i5-8250U processor 1.60 GHz (4 cores, 8 threads), 7.5 GB RAM
  running Ubuntu 18.04.4 LTS 64-bit \textcolor{red}{and an SSD
    drive}. \textcolor{red}{The data used for the benchmarking are a
    TMT 4-plex experiment acquired on a LTQ Orbitrap Velos (Thermo
    Fisher Scientific) available in the \texttt{msdata} package and
    described in \citep{Gatto:2014}.}}
\label{fig:bench}
\end{figure}
